### 2015-08-23 V4046Sgr2013/ms_v4046sgr2013_chapter.tex
chapter 2 summary
fixed figure placement

\chapter{The Structure of the Evolved Circumbinary Disk around V4046 Sgr}{\label{c:v4046_structure}

\section*{abstract}
We present sensitive, sub-arcsecond resolution Submillimeter Array observations 
of the protoplanetary disk around the nearby, pre-main sequence spectroscopic 
binary V4046 Sgr.  We report for the first time a large inner hole ($r=29$\,AU) 
spatially resolved in the 1.3\,mm continuum emission and study the structure of 
this disk using radiative transfer calculations to model the spectral energy
distribution (SED), continuum visibilities, and spectral line emission of CO and
its main isotopologues.  Our modeling scheme demonstrates that the majority of 
the dust mass is distributed in a narrow ring (centered at 37\,AU with a FWHM of
16\,AU) that is $\sim$5$\times$ more compact than the gas disk.  This structure 
implies that the dust-to-gas mass ratio has a strong spatial variation, ranging 
from a value much larger than typical of the interstellar medium (ISM) at the 
ring to much smaller than that of the ISM at larger disk radii.  We suggest that
these basic structural features are potentially observational signatures of the 
accumulation of solids at a local gas pressure maximum.  These models also 
require a substantial population of $\sim$$\mu$m-sized grains inside the central
disk cavity.  We suggest that this structure is likely the result of dynamical 
interactions with a low-mass companion, although photoevaporation may also play 
a secondary role.

>>>>

\chapter{The Structure of the Evolved Circumbinary Disk around V4046 Sgr}{\label{chap:v4046sgr_structure}

%%\section*{abstract}
In this chapter we present sensitive, sub-arcsecond resolution Submillimeter Array observations 
of the protoplanetary disk around the nearby, pre-main sequence spectroscopic 
binary V4046 Sgr.  We report for the first time a large inner hole ($r=29$\,AU) 
spatially resolved in the 1.3\,mm continuum emission and study the structure of 
this disk using radiative transfer calculations to model the spectral energy
distribution (SED), continuum visibilities, and spectral line emission of CO and
its main isotopologues.  Our modeling scheme demonstrates that the majority of 
the dust mass is distributed in a narrow ring (centered at 37\,AU with a FWHM of
16\,AU) that is $\sim$5$\times$ more compact than the gas disk.  This structure 
implies that the dust-to-gas mass ratio has a strong spatial variation, ranging 
from a value much larger than typical of the interstellar medium (ISM) at the 
ring to much smaller than that of the ISM at larger disk radii.  We suggest that
these basic structural features are potentially observational signatures of the 
accumulation of solids at a local gas pressure maximum.  These models also 
require a substantial population of $\sim$$\mu$m-sized grains inside the central
disk cavity.  We suggest that this structure is likely the result of dynamical 
interactions with a low-mass companion, although photoevaporation may also play 
a secondary role.

### 2015-08-23 hd163296/ms_hd163296_chapter.tex
finished rough conclusion draft
fixed figure placement

\chapter{A Spatially Resolved Vertical Temperature Gradient in the HD 163296 Disk}\label{c:hd163296}

\section*{abstract}
We analyze sensitive, sub-arcsecond resolution ALMA Science Verification 
observations of CO emission lines in the protoplanetary disk hosted by the 
young, isolated Ae star HD 163296.  The observed spatial morphology of the 
$^{12}$CO $J$=3$-$2 emission line is asymmetric across the major axis of the 
disk; the $^{12}$CO $J$=2$-$1 line features a much less pronounced, but similar,
asymmetry.  The $J$=2$-$1 emission from $^{12}$CO and its main isotopologues 
have no resolved spatial asymmetry.  We associate this behavior as the direct 
signature of a vertical temperature gradient and layered molecular structure in 
the disk.  This is demonstrated using both toy models and more sophisticated 
calculations assuming non-local thermodynamic equilibrium (non LTE) conditions. 
A model disk structure is developed to reproduce both the distinctive spatial 
morphology of the $^{12}$CO $J$=3$-$2 line as well as the $J$=2$-$1 emission 
from the CO isotopologues assuming relative abundances consistent with the 
interstellar medium.  This model disk structure has $\tau=1$ emitting surfaces 
for the $^{12}$CO emission lines that make an angle of $\sim 15^\circ$ with 
respect to the disk midplane.  Furthermore, we show that the spatial and 
spectral 
sensitivity of these data can distinguish between models that have 
sub-Keplerian gas velocities due to the vertical extent of the disk and its 
associated radial pressure gradient (a fractional difference in the bulk gas 
velocity field of $\gtrsim 5$\%).

>>>>

\chapter{A Spatially Resolved Vertical Temperature Gradient in the HD 163296 Disk}\label{chap:hd163296}

%%\section*{abstract}
In this chapter we analyze sensitive, sub-arcsecond resolution ALMA Science Verification 
observations of CO emission lines in the protoplanetary disk hosted by the 
young, isolated Ae star HD 163296.  The observed spatial morphology of the 
$^{12}$CO $J$=3$-$2 emission line is asymmetric across the major axis of the 
disk; the $^{12}$CO $J$=2$-$1 line features a much less pronounced, but similar,
asymmetry.  The $J$=2$-$1 emission from $^{12}$CO and its main isotopologues 
have no resolved spatial asymmetry.  We associate this behavior as the direct 
signature of a vertical temperature gradient and layered molecular structure in 
the disk.  This is demonstrated using both toy models and more sophisticated 
calculations assuming non-local thermodynamic equilibrium (non LTE) conditions. 
A model disk structure is developed to reproduce both the distinctive spatial 
morphology of the $^{12}$CO $J$=3$-$2 line as well as the $J$=2$-$1 emission 
from the CO isotopologues assuming relative abundances consistent with the 
interstellar medium.  This model disk structure has $\tau=1$ emitting surfaces 
for the $^{12}$CO emission lines that make an angle of $\sim 15^\circ$ with 
respect to the disk midplane.  Furthermore, we show that the spatial and 
spectral 
sensitivity of these data can distinguish between models that have 
sub-Keplerian gas velocities due to the vertical extent of the disk and its 
associated radial pressure gradient (a fractional difference in the bulk gas 
velocity field of $\gtrsim 5$\%).
